TODO

### 2022-12-09 code/annotation_analysis.Rmd
some model summaries

library(here)
library(tidyverse)
#library(rstanarm)
library(rstan)
library(tidybayes)
library(viridis)
library(cowplot)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
#for plotting
theme_set(theme_bw())
#Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")
read_data_path <- "data/processed_data/joined_data/"
annotation_path <- "data/annotations"
model_path <- "code/models"

show_summary_rstan <- function(model){
  badlist <- c("accept_stat__","divergent__","energy__","n_leapfrog__","sigma", "stepsize__","treedepth__")
  intervals <- gather_draws(model, `[a-zA-z_()]+`, regex=TRUE) |> mean_qi() |> filter(!.variable %in% badlist) |> 
    mutate(lower=round(.lower, digits=2),
           upper=round(.upper, digits=2),
           `Credible Interval`=str_c("[",lower,", ", upper,"]"),
           Term=.variable,
           Estimate=round(.value, digits=2)) %>% 
    select(Term, Estimate, `Credible Interval`)

@@

m1 <- stan_lmer(numword ~ trialNum + condition + (1|gameId)+ (1|player)+(1|flower), data=annotated) |> write_rds(here(model_path,"m1.rds"))

@@

```{r, eval=F, include=F}
m1 <- read_rds(here(model_path,"m1.rds"))
m1
#prior_summary(m1)
show_summary_rstan(m1)
```

@@

# by trial
flower_all <- M_mat %>% 
  filter(seen %in% c("game")) |> 
  group_by(color,condition) %>% 
  mutate(combinedId=str_c(referent,"_", trialNum, "_",gameId,"_",playerId))
  make_across_df(F_mat, 'cosine') 
  separate(dim1, c("ref1", "trialNum1","game1","player1"), convert=T) |> 
  separate(dim2, c("ref2", "trialNum2", "game2", "player2"), convert=T) |> 
 # rename(referent1=dim1,referent2=dim2) %>% 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  #filter(ref1!=ref2) %>% 
  mutate(earlier=ifelse(trialNum1>trialNum2,trialNum2, trialNum1) |> as.numeric(),
         later=ifelse(trialNum1>trialNum2, trialNum1,trialNum2) |> as.numeric()) |> 
  ungroup()
```

@@

>>>>

library(here)
library(tidyverse)
library(rstanarm)
library(rstan)
library(tidybayes)
library(viridis)
library(cowplot)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
#for plotting
theme_set(theme_bw())
#Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")
read_data_path <- "data/processed_data/joined_data/"
annotation_path <- "data/annotations"
model_path <- "code/models"

show_summary_rstan <- function(model){
  badlist <- c("accept_stat__","divergent__","energy__","n_leapfrog__","sigma", "stepsize__","treedepth__")
  intervals <- gather_draws(model, `[a-zA-z_(): ]+`, regex=TRUE) |> mean_qi() |> filter(!.variable %in% badlist) |> 
    mutate(lower=round(.lower, digits=2),
           upper=round(.upper, digits=2),
           `Credible Interval`=str_c("[",lower,", ", upper,"]"),
           Term=.variable,
           Estimate=round(.value, digits=2)) %>% 
    select(Term, Estimate, `Credible Interval`)

@@

m1 <- stan_lmer(numword ~ trialNum + condition + (1|gameId)+ (1|player)+(1|flower), data=annotated) |> write_rds(here(model_path,"m1.rds"))
show_summary_rstan(m1) |> write_rds(here(model_path,"word_model.rds"))
```

```{r, eval=F, include=F}
m1 <- read_rds(here(model_path,"m1.rds"))
m1

@@

@@

# by trial
flower_all <- M_mat %>% 
  filter(seen %in% c("game")) |> 
  group_by(color,condition) %>% 
  mutate(combinedId=str_c(referent,"_", trialNum, "_",gameId,"_",playerId)) |> 
  make_across_df(F_mat, 'cosine') |> 
  separate(dim1, c("ref1", "trialNum1","game1","player1"), convert=T) |> 
  separate(dim2, c("ref2", "trialNum2", "game2", "player2"), convert=T) |> 
 # rename(referent1=dim1,referent2=dim2) %>% 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  #filter(ref1!=ref2) %>% 
  mutate(earlier=ifelse(trialNum1>trialNum2,trialNum2, trialNum1) |> as.numeric(),
         later=ifelse(trialNum1>trialNum2, trialNum1,trialNum2) |> as.numeric()) |> 
  ungroup()
```

@@

```
### Model

```{r, eval=F}
within_game_flower <- flower_all |> 
  filter(game1==game2) |> 
  filter(ref1==ref2) |> 
  filter(later-earlier<3) |> 
  mutate(same_player=ifelse(player1==player2,1,0),
         flower=str_c(color,ref1)) |> 
  select(sim, condition, earlier, same_player, game1, flower )

m_samegame_sameflower <-  stan_lmer(sim ~ condition*earlier*same_player + 
                                      (1|game1)+(1|flower), data=within_game_flower) |> write_rds(here(model_path,"m2.rds"))

show_summary_rstan(m_samegame_sameflower) |> write_rds(here(model_path,"samegame_sameflower_model.rds"))

```{r, eval=F}
within_game_between_flower <- flower_all |> 
  filter(game1==game2) |> 
  filter(ref1!=ref2) |> 
  filter(later-earlier<3) |> 
  mutate(same_player=ifelse(player1==player2,1,0)) |> 
  select(sim, condition, earlier, same_player, game1)

m_samegame_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=within_game_between_flower) |> write_rds(here(model_path,"m3.rds"))

show_summary_rstan(m_samegame_diffflower) |> write_rds(here(model_path,"samegame_diffflower_model.rds"))

```{r}
between_game_within_flower <- flower_all |> 
  filter(game1!=game2) |> 
  filter(ref1==ref2) |> 
  filter(later-earlier<3) |> 
  mutate(flower=str_c(color,ref1)) |> 
  select(sim, condition, earlier, flower)

m_diffgame_sameflower <-  stan_glm(sim ~ condition*earlier, data=between_game_within_flower) |> write_rds(here(model_path,"m4.rds"))

show_summary_rstan(m_diffgame_sameflower) |> write_rds(here(model_path,"diffgame_sameflower_model.rds"))

### 2022-12-09 write-ups/cogsci23_paper/manuscript.Rmd
some model summaries

@@

@@

@@

per_person <- annotated |> group_by(gameId, trialNum, condition, player, name) |> select(flower) |> unique() |> tally() |> full_join(d.rounds.final) |> 
  mutate(n=ifelse(is.na(n),0,n))
mean_person <- per_person |> group_by(condition) |> summarize(mean=mean(n) |> round(2), sd=sd(n) |> round(2), summ=str_c(mean," (sd: ",sd,")")) |> 
  select(condition, summ)
```
Consistent with the results from dyadic iterated reference games, the amount of referring language decreases over the course of the game. As shown in Fig @ref(fig:wordcount)A, the number of words of referring language decreases across the game in both conditions. This is due to the individual referring expressions getting shorter (@ref(fig:wordcount)B), while the total number of referring epxressions remains that same (@ref(fig:wordcount)C).

@@

>>>>

# TODOs
redraft intro & add citations
add figs
learn stan and run models
redraft methods
write analysis
write discussion
abstract & front matter

@@

## SBERT embeddings

@@

For the pairwise comparisons of utterances during the game, we take the similarities for utterances that are within 2 trials of each other (ex. an utterance from trial 10 is compared with utterances from trials 8,9,10,11,12). We do this because different flowers were shown to different groups on different trials. This width is a compromise between having enough pairs of utterances and still being able to treat them as coming from one time point in the game.

@@

per_person <- annotated |> group_by(gameId, trialNum, condition, player, name) |> select(flower) |> unique() |> tally() |> full_join(d.rounds.final) |> 
  mutate(n=ifelse(is.na(n),0,n))
mean_person <- per_person |> group_by(condition) |> summarize(mean=mean(n) |> round(2), sd=sd(n) |> round(2), summ=str_c(mean," (sd: ",sd,")")) |> 
  select(condition, summ)
```

```{r,eval=F, include=F}

m1 <- stan_lmer(numword ~ trialNum + condition + (1|gameId)+ (1|player)+(1|flower), data=annotated) |> write_rds(here(model_path,"m1.rds"))
show_summary_rstan(m1) |> write_rds(here(model_path,"word_model.rds"))
```

```{r}

word_count <- read_rds(here(model_path,"word_model.rds"))
```

Consistent with the results from dyadic iterated reference games, the amount of referring language decreases over the course of the game. As shown in Fig @ref(fig:wordcount)A, the number of words of referring language decreases across the game in both conditions. This is due to the individual referring expressions getting shorter (@ref(fig:wordcount)B), while the total number of referring epxressions remains that same (@ref(fig:wordcount)C).

@@

```{r}
wi_g_wi_f <- read_rds(here(model_path,"samegame_sameflower_model.rds"))

#wi_g_bet_f <- read_rds(here(model_path,"samegame_diffflower_model.rds"))

#bet_g_wi_f <- read_rds(here(model_path,"diffgame_sameflower_model.rds"))
```

### Within games
TODO we compare games within 2 rounds of each other (ex. trial 10 compared to 8, 9, 10, 11, 12)

One of the key claims is that within a partnership, the referring expressions should converge for the same image, but get more different for different images. Convergence would be increasing similiarity (higher cosine similarity in later rounds), divergence would be decreasing similarity in later rounds).

For the same flower within the same game, similarity increased over rounds (trial: `r stats_text(wi_g_wi_f,6)`). Utterances were more similar if they were produced by the same participant (`r stats_text(wi_g_wi_f,8)`), although this did not interact with trial number (`r stats_text(wi_g_wi_f,7)`). Games in the shared utilities condition may have had higher similarities overall (`r stats_text(wi_g_wi_f,2)`), but this did not interact with trial number (`r stats_text(wi_g_wi_f,3)`) or same participant versus different participant (`r stats_text(wi_g_wi_f,5)`).

same person 
condition
interactions w/ trial

### Between games
